E4-analysis-comparison-to-original

### 2024-11-02 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
Exps 3 and 4, mostly

```{r plot subjects by validation-JH, eval=F}
#printed? No: eval=F
ggplot(jh.validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
```{r E1b-calib-effect, fig.cap='Calibration scores in Exp. 1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
#I picked this one because it's the same as in E1a
ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

>>>>

```{r plot subjects by validation-JH, eval=F, out.width="50%", fig.align="center"}
#printed? No: eval=F
ggplot(jh.validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
```{r E1b-calib-effect, fig.cap='Calibration scores in Exp. 1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.', out.width="50%", fig.align="center"}
#I picked this one because it's the same as in E1a
ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E1b-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}

### 2024-11-02 group-a/E1-analysis-replication.Rmd
Exps 3 and 4, mostly

```{r plot subjects by validation, eval=F}
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

```{r make remote spaghetti plot}

@@

```{r eval=FALSE, include=FALSE}
E1_first_fix_plot <- ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).'}
#I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
ggplot(cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

>>>>

```{r plot subjects by validation, eval=F, out.width="50%", fig.align="center"}
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

```{r make remote spaghetti plot, out.width="50%", fig.align="center"}

@@

```{r eval=FALSE, include=FALSE, out.width="50%", fig.align="center"}
E1_first_fix_plot <- ggplot(first.fixation.after.verb.onset.summary.min, aes(x=verb_type, y=m, ymin=m-se,ymax=m+se))+
  geom_col()+
  geom_errorbar(width=0.2)
```

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against the verb effect on first fixations (the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition).', out.width="50%", fig.align="center"}
#I picked this one because the DV is easiest to explain, and because it's the DV where the effect comes out once you drop the "bad" participants
ggplot(cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E1a-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions.", out.width="50%", fig.align="center"}

### 2024-11-02 group-b/E2-analysis-calibration.Rmd
Exps 3 and 4, mostly

```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).'}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
  geom_point()+
  geom_smooth(method = "lm", formula = y ~ x) +
  labs(x="Calibration Score", y="Gaze Bias")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

>>>>

```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).', out.width="50%", fig.align="center"}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
  geom_point()+
  geom_smooth(method = "lm", formula = y ~ x) +
  labs(x="Calibration Score", y="Gaze Bias")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

### 2024-11-02 group-b/E2-analysis-replication.Rmd
Exps 3 and 4, mostly

```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE}
fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic(base_size = 25)+
  coord_cartesian(ylim = c(0, 0.4))+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig
```
```{r saving plot, eval=FALSE}
saveRDS(fig, "output/ETfig.rds")
ggsave("output/ETfig.png", plot = fig, width  = 8.5, height = 5.5)
```

```{r}
view.summary.condition1.data <- view.summary.subject.data %>%
  group_by(normalized_quadrant, condition) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```
```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions."}

@@

```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F}
fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig.fixed
```

@@

```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval."}
acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")
acc_rt_fig
```

>>>>

```{r E2-gaze-fig-free, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval =FALSE, out.width="50%", fig.align="center"}
fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic(base_size = 25)+
  coord_cartesian(ylim = c(0, 0.4))+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig
```
```{r saving plot, eval=FALSE}
saveRDS(fig, "output/ETfig.rds")
ggsave("output/ETfig.png", plot = fig, width  = 8.5, height = 5.5)
```

```{r}
view.summary.condition1.data <- view.summary.subject.data %>%
  group_by(normalized_quadrant, condition) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```
```{r E2-gaze-fig-both-conds, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants during memory retrieval in a) fixed and b) free viewing conditions.", out.width="50%", fig.align="center"}

@@

```{r E2-gaze-fig-fixed, fig.cap = "Proportion of eye-gaze to critical quadrant and other three quadrants durign memory retrieval.", eval = F, out.width="50%", fig.align="center"}
fig.fixed<-ggplot(fixed.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig.fixed
```

@@

```{r E2-rt-acc-fig, fig.cap = "Accuracy and response times during memory retrieval.", out.width="50%", fig.align="center"}
acc_rt_fig<-acc_fig + rt_fig + plot_layout(guides = "collect")
acc_rt_fig
```

### 2024-11-02 group-c/E3-analysis-calibration.Rmd
Exps 3 and 4, mostly

To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant. The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed.

Calibration scores were not correlated with looking scores, regardless of whether scores were computed using the halves coding method (see Figure \ \@ref(fig:E3-cal-Plot-looking-score-(halves)-by-calibration) or the ROI coding method (see  Figure \ \@ref(fig:E3-cal-Plot-looking-score-(roi)-by-calibration)).

```{r E3-cal-Plot-looking-score-(halves)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).'}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E3-cal-Plot-looking-score-(roi)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).'}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (ROIs)") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures. None of the four relationships showed a significant correlation (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).

```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance. Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).'}
# Set up facet label names for behavioral_measure variable
behav.labs <- c("Confidence", "Reaction Time")
names(behav.labs) <- c("confidence", "rt")

@@

#### Re-analysis After Exclusions
As is clear from the preceding figures, there was a large number of participants (N = `r e2.n.bad.subjects.aggro`) that had calibration scores under 50%. When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-e2.n.bad.subjects.aggro`), key results were aligned with the main analyses. The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

>>>>

To see if calibration success is correlated with the eye tracking effects, we calculated a calibration score for each participant. The calibration score was the average proportion of samples within 200 pixels of the validation points during the final validation phase before the eye tracking is performed. Calibration scores were not correlated with proportion looks to novel, regardless of whether scores were computed using ROIs (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-roi-by-calibration)) or split-halves (see Figure\ \@ref(fig:E3-cal-Plot-looking-score-halves-by-calibration).

```{r E3-cal-Plot-looking-score-halves-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).', out.width="50%", fig.align="center"}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score halves")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

```{r E3-cal-Plot-looking-score-roi-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).', out.width="50%", fig.align="center"}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (ROIs)") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

Similarly, there was no correlation between calibration scores with the correlation between day 2 memory performance and day 1 looking for either kind of behavioral and looking measures (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).

```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance. Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).', out.width="50%", fig.align="center"}
# Set up facet label names for behavioral_measure variable
behav.labs <- c("Confidence", "Reaction Time")
names(behav.labs) <- c("confidence", "rt")

@@

#### Re-analysis After Exclusions
As is clear from the preceding figures, there was a large number of participants (N = `r e3.bad.subjects.validation.aggro`) that had calibration scores under 50%. When we re-analyzed the subset that remained after those participants were excluded (N = `r 45-n.e3.bad.subjects.validation.aggro`), key results were aligned with the main analyses. The looking score result was upheld such that participants looked more at the new image on Day 1 (mean: `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`) (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`)), but looking scores remained unrelated to Day 2 memory outcomes (confidence: t(`r looking.confidence.correlation.t.test.aggro$parameter`) = `r looking.confidence.correlation.t.test.aggro$statistic`, p = `r looking.confidence.correlation.t.test.aggro$p.value`; RT: t(`r  looking.rt.correlation.t.test.aggro$parameter`) = `r looking.rt.correlation.t.test.aggro$statistic`, p = `r looking.rt.correlation.t.test.aggro$p.value`).

### 2024-11-02 group-c/E3-analysis-roi.Rmd
Exps 3 and 4, mostly

In the original experiment, the two objects on day 1 were presented on two separate monitors and gaze was coded by manually coding video recordings. In our replication analysis, we analyzed eye movement data using ROIs defined around the two images. In this section we explore an alternative coding of the eye movement data by coding simply left half vs. right half of the screen. The coarser coding may be more appropriate for webcam-based eyetracking.

@@

The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score).

```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves."}
ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
  theme_bw()+
  coord_fixed()+
  theme(panel.grid=element_blank())
```

#### Looking Scores

@@

When looking scores are coded as left vs. right half of the screen, we find that participants looked more at the novel object. The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`). This was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.

@@

```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

#### Correlations with Day 2 Performance

>>>>

@@

Above we excluded looks that fell outside the ROIs. In contrast, the original experiment simply coded looks as being to the left or right. This may be more appropriate to the limited resolution of camera-based eye-gaze detection. We re-ran analyses based on this split-half coding criterion. The correlation between looking scores using the ROI method and the halves method is `r ls.cor` (see Figure\ \@ref(fig:E3-roi-correlation-of-looking-score)).

```{r E3-roi-correlation-of-looking-score, echo=FALSE, fig.cap="Correlation between looking scores calculated using ROIs and using screen halves.", out.width="50%", fig.align="center"}
ggplot(looking.score.data %>% filter(!is.nan(looking.score.roi)), aes(x=looking.score.roi, y=looking.score.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  labs(x="Looking Score (ROIs)", y="Looking Score (Halves)")+
  theme_bw()+
  coord_fixed()+
  theme(panel.grid=element_blank())
```

@@

We again found that participants looked more at the novel object, though at a slightly lower rate than before (`r mean(t.test.data1$M.looking.score)`; *SD* = `r sd(t.test.data1$M.looking.score)`). As before, this was significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`.

@@

```{r E3-roi Plot of cumulative looking score, echo=FALSE, eval = FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM.", out.width="50%", fig.align="center"}
#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

### 2024-11-02 group-d/E4-analysis-ROIs.Rmd
Exps 3 and 4, mostly

```{r, eval = F}

@@

```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants. Magenta points indicate looks that were not categorized into an ROI."}
p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")
p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+ 
  theme_bw()+
  theme(legend.position = "none")

@@

```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image). Vertical lines indicate average onsets of animal and instrument offset by 200ms."}

@@

Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \@ref(fig:E4-gaze-timecourse-fig-quadrants)).  In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`). Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.

>>>>

```{r, eval = F, out.width="50%", fig.align="center"}

@@

```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants. Magenta points indicate looks that were not categorized into an ROI.", out.width="65%", fig.align="center"}
p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")
p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+ 
  theme_bw()+
  theme(legend.position = "none")

@@

```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image). Vertical lines indicate average onsets of animal and instrument offset by 200ms.", out.width="50%", fig.align="center"}

@@

Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \@ref(fig:E4-gaze-timecourse-fig-quadrants)).  In the _post-instrument_ window, participants's proportion of looks to the target animal in the modifier-biased condition and the equi-biased conditions were significantly greater than inthe instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`). Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.

### 2024-11-02 group-d/E4-analysis-calibration.Rmd
Exps 3 and 4, mostly

```{r, eval = F}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject))+
  theme_bw()+
  theme(legend.position = "none") 
```
```{r, eval=F}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject, names_from=calib_num, values_from = mean_percent_in_roi )

@@

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

@@

```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x="Calibration Score", y="Bias Effect") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).

@@

```
#### Re-analysis After Exclusions
Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset. Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).

>>>>

```{r, eval = F, out.width="50%", fig.align="center"}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject))+
  theme_bw()+
  theme(legend.position = "none") 
```

```{r, eval=F, out.width="50%", fig.align="center"}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject, names_from=calib_num, values_from = mean_percent_in_roi )

@@

```{r, eval = F, out.width="50%", fig.align="center"}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

@@

```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).', out.width="50%", fig.align="center"}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x="Calibration Score", y="Bias Effect") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).

@@

```
#### Re-analysis After Exclusions
Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset. Participants' preference to the target animal relative to the target instrument in the modifier-biased condition and the equi-biased conditions was greater than in the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001), but the difference betwen the modifier biased condition and the equi-biased condition was not significant ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2024-11-02 group-d/E4-analysis-comparison-to-original.Rmd
Exps 3 and 4, mostly

ggplot(bind_rows(first.move.orig.summary, first.move.web.summary), 
       aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE, alpha = study))+
  geom_col(position=position_dodge(width=0.9), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
  scale_alpha_manual(values = c(0.5,1))+
  coord_cartesian(ylim = c(0,1))+
  theme_classic()+
  labs(y = "Proportion of first mouse movements", x = "Bias")
```

>>>>

ggplot(bind_rows(
  first.move.orig.summary %>% mutate(study_type = "Original"),
  first.move.web.summary %>% mutate(study_type = "Web")), 
  aes(x=bias, fill=target_type, y=M, ymin=M-SE, ymax=M+SE)) +
  geom_col(position=position_dodge(width=0.9), color = "black") +
  geom_errorbar(position=position_dodge(width=0.9), width=0.2) +
  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other")) +
  coord_cartesian(ylim = c(0,1)) +
  theme_classic() +
  labs(y = "Proportion of first mouse movements", x = "Bias") +
  facet_wrap(~study_type, ncol = 1)  # This creates vertical panels
```
